An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-17 draft.tex
Intro to Proposed method

>>>>

In this section, we present the design
and a container-based implementation of the model we propose for the execution
of multi-population based algorithms. We follow the requirements outlined in
Section \ref{multi} and the general design principles of cloud-native
applications we have mention earlier. As a first step, we describe the general
architecture first, and then we describe each component in detail. The primary
data element used throughout the system is the subpopulation, and at a higher
level, we can view the system as a continuous stream of subpopulations flowing
from one process to the other. By "continuous stream," we mean that ideally,
everything must happen asynchronously without components needing to wait for
others. In this kind of system, this streaming functionality is normally
implemented by using a message queue system. For instance, if one process needs
to communicate a subpopulation to another, it must pack the sub-population into
a message, and then push the message asynchronously to the queuing system; this
means that after the process pushes the message, it continues its execution
without waiting for a result. On the other end, a recipient subscribes to the
message queue by defining an event handler method that is triggered when a
message is pushed to the queue. The two components at each end of the queue are
Producers that push messages to the queue and Consumers that pull them. This
pattern is an essential component of a reactive architecture because it is
highly scalable; one of the reasons for this are stateless functions. We can
define stateless functions as methods that do not have side effects, meaning
they do not need to read, keep, or modify data outside of the method. If
Consumers are implemented using stateless functions, then there is no difference
in having one or many copies of the function pulling work from the queue at the
same time, because no side effects are resulting from the concurrency.  
Based on a reactive architecture we proposed in a previous work
\cite{guervos2018introducing}, we now describe the general architecture shown in
Figure .
